Grade Retention and Mixed Race

### 2022-11-11 products/paper/main.qmd
Update bibliography for previous changes

Discrimination and bias by race play an important role in overall levels of racial inequality [@quillian_new_2006; @pager_sociology_2008]. Discrimination need not be consciously recognized by actors, but may instead reflect cognitive biases and schema that individuals unknowningly rely upon and reinforce in social interactions @quillian_new_2006]. Such discrimination will be most consequential when performed by important gatekeepers of opportunity such as teachers, health care workers, and employers. Discrimination need not just occur on an individual basis, but can also be systemic in nature when biases are built into and reinforced by organizations and institutional systems [@reskin_race_2012]. In our current "colorblind" regime [@bonilla-silva_racism_2006], such systems may be formally race neutral but produce disparate impacts by race [@pager_sociology_2008].

>>>>

Discrimination and bias by race play an important role in overall levels of racial inequality [@quillian_new_2006; @pager_sociology_2008]. Discrimination need not be consciously recognized by actors, but may instead reflect cognitive biases and schema that individuals unknowningly rely upon and reinforce in social interactions [@quillian_new_2006]. Such discrimination will be most consequential when performed by important gatekeepers of opportunity such as teachers, health care workers, and employers. Discrimination need not just occur on an individual basis, but can also be systemic in nature when biases are built into and reinforced by organizations and institutional systems [@reskin_race_2012]. In our current "colorblind" regime [@bonilla-silva_racism_2006], such systems may be formally race neutral but produce disparate impacts by race [@pager_sociology_2008].
